A comparison of classification algorithms applied to the Adult Database

### 2009-12-10 report/final.tex
preliminary vesion of the introduction.

>>>>

Current real-world databases are rich with information that can be used for
decision making. Classification is a form of data analysis used to extract 
models that describe important data classes \cite{2}. Classification is, thus, 
the process of predicting categorical labels. There has been active research on 
the fields of machine learning, pattern recognition and statistics regarding 
classification. Data classification is a two-step process, involving both a 
learning step and a training step. The learning step builds a model, or 
classifier, from training data, to which the class is already known (therefore
this is called supervised learning, as opposed to unsupervised learning used in
clustering, for example). The training step evaluates the accuracy of the 
classifier by providing data not used on the learning step. If the accuracy is
considered acceptable, then the rules can be applied to the classification of
new data tuples.

The models built can assume different forms, ranging from decision trees to 
classification rules, including prolog clauses (as in ILP \cite{ilp}). This
report describes the application of different classification algorithms applied
to the adult database. It starts by identifying the problem, describing the
algorithms to be applied, the data format, the experimental context and the 
experimental evaluation. Some conclusions are then taken on the subject and 
related work is described.
